---
title: "satRdays: a snarky correlation function"
author: "Patrick Durkee"
date: 2019-01-12 
categories: ["satRdays"]
tags: ["satRdays"]
---

There are a lot of ways to do correlations in R (I use `corr.test` most of the time), but I just found out about the function, `correlation`, from the `psycho` package and it might be my new favorite. I give a quick tutorial of it here (see the [The Psycho Blog](https://neuropsychology.github.io/psycho.R/2018/05/20/correlation.html) for the developers' tutorial).


## Tutorial
If you're following along, you'll need to install the package from github:
```{r install, warning=FALSE, message=F, eval=F, echo=T}
# install.packages("devtools")
devtools::install_github("neuropsychology/psycho.R") # installs newest version
library(psycho)
```

Now let's see it in action using the `mtcars` dataset, which contains data on fuel consumption for various car models made in 1974 (super exciting, I know). 

```{r data}

head(mtcars) # this dataset is preloaded in R

```

Imagine we have a ~~hunch~~ hypothesis that car weight (`wt`) will be negatively associated with fuel efficiency (`mpg`). The `correlation` package prints out the results in a manuscript-ready format.

```{r testcor}

psycho::correlation(mtcars[, c('mpg', 'wt')])

```

The `correlation` package also makes it easy to create formatted correlation matrices---complete with cute little significance stars. Let's look at the correlations between a few more totally-theory-driven metrics.

```{r matrixtable, echo=T}
cors <- psycho::correlation(mtcars[, c('mpg', 'cyl', 'hp','wt', 'disp')])
cortable <- summary(cors)
# if you want to save it to excel run this
# write.csv(cortable, "correlationtable.csv") 
# cortable
knitr::kable(cortable) # you don't need this: the `kable` function just makes it pretty for html rendering
```

We can also quickly make a nice little plot of the correlations to share with collaborators:
```{r plot}
plot(cors)
```

### Alpha correction
You may have noticed earlier that `correlation` package automatically applies p-value corrections to the correlations. The default is Holm's method, but you can specify others by setting the `adjust = ` argument to 'bonferroni', 'fdr', or 'none'. It doesn't change much, in this case.

```{r correction}
boncors <- psycho::correlation(mtcars[, c('mpg', 'cyl', 'hp','wt', 'disp')],
                            adjust = 'bonferroni')
boncortable <- summary(boncors)
knitr::kable(boncortable) 
```

### The 'snarky' part
So all that is pretty cool, but the main reason I like the `correlation` package is because it trolls you if you get too carried away with correlations. 

Let's imagine we were just fishing around for some significant correlations (i.e., totally normal science stuff) so we just ran all possible pairwise correlations in the `mtcars` dataset[^1]; we wouldn't want any pesky alpha corrections getting in the way of discovering an intersting correlation, so let's make sure we set that `adjust` argument to 'none'. 

```{r fishing}
allcors <- psycho::correlation(mtcars, adjust = 'none')
allcorstable <- summary(allcors)
knitr::kable(allcorstable) 
```

Now we think to ourselves: 

> "Wow look at all those super intersting significant correlations we found! But wait, what's going on with these extra variables that aren't in the original dataset!? We didn't collect data on Schopenhauers Optimism or Local Air Density..."

#### What's going on?
To make it harder to *accidentally* run too many uncorrected tests, the `correlation` function simuluates new random variables (complete with funny names) when you run more than 10 uncorrected correlations. If you're deadset on p-hacking, you can override this by setting the `i_am_cheating` argument to `TRUE`.

```{r cheating}
allcors <- psycho::correlation(mtcars, adjust = 'none', i_am_cheating = TRUE)
allcorstable <- summary(allcors)
knitr::kable(allcorstable) 
```

There, now you can publish all those super significant, intersting, real, and totally *a-priori* correlations you found without all those spurious ones that the `correlation` package created... (just make sure to hide your code from reviewers!)

## Conclusion
Lame p-hacking/fishing jokes aside, the `correlation` package is really easy to use and makes reporting more efficient and reproducible. It's just an added benefit that it  also makes it a little harder to unknowingly/passively run a bunch of uncorrected (and potentially spurious) correlations. I think it would be cool to see more packages set defaults that are explicitly aimed at reducing questionable research practices. 

Know of any others? Let me know about them at pdurkee@utexas.edu or @durkeepk so I can learn them.

[^1]: A bunch of the variables in `mtcars` are dichotomous or categorical so this doesn't make much sense, but bare with me because that's not the point.
