\documentclass[10pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}

\usepackage{etaremune}
\usepackage{enumitem}
\setlist[enumerate]{nosep} % To remove the spacing


% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}


% Make parskips rather than indent with lists.
\usepackage{parskip}

\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
%\usepackage[en-US]{datetime2}
\usepackage{datetime2}

\makeatletter
%\newcommand{\monthyeardate}{\DTMlangsetup{showdayofmonth=false}\today}
%\newcommand{\monthyeardate}{\DTMlangsetup{\@dtm@month}}

%\DTMenglishmonthname{\@dtm@month}}
%\makeatother
%\lfoot{\scriptsize \DTMlangsetup{\@dtm@month}}
\lfoot{\scriptsize August, 2025}
%\lfoot{\scriptsize \monthyeardate}
\cfoot{\scriptsize Patrick Durkee | CV }
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Patrick Durkee:  CV (Curriculum Vitae)},
            pdfauthor={Patrick Durkee},
            pdfkeywords={RMarkdown, academic CV, template},
            colorlinks=true,
            linkcolor=black,
            citecolor=Blue,
            urlcolor=black,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Patrick Durkee}

\vspace{2 mm}

\hrule

\vspace{2 mm}



\moveleft.5\hoffset\centerline{ 
\faEnvelope \hspace{1 mm} \href{mailto:}{\tt \href{mailto:pdurkee@csufresno.edu}{\nolinkurl{pdurkee@csufresno.edu}}} \hspace{1 mm} 
   
\faGlobe \hspace{1 mm} \href{http://pdurkee.com}{\tt pdurkee.com}  \hspace{1 mm}   
\faGithub \hspace{1 mm} \href{http://github.com/durkeepk}{\tt durkeepk} \hspace{1 mm} 
\faTwitterSquare \hspace{1 mm} \href{http://twitter.com/durkeepk}{\tt durkeepk} 

}

\vspace{2 mm}

\hrule


\definecolor{light-gray}{gray}{.5}

\section{PROFESSIONAL APPOINTMENTS}\label{professional-appointments}

Assistant Professor of Psychology, \emph{California State University,
Fresno} \hfill \textcolor{light-gray}{2023 - Present}

Research Fellow, \emph{Institute for Advanced Study in Toulouse, France}
\hfill \textcolor{light-gray}{2022 - 2023}

Adjunct Professor of Psychology, \emph{Texas State University}
\hfill \textcolor{light-gray}{2021 - 2022}

\section{EDUCATION}\label{education}

Ph.D., Psychology, \emph{The University of Texas at Austin}
\hfill \textcolor{light-gray}{2021}

M.A., Experimental Psychology, \emph{California State University,
Fullerton} \hfill \textcolor{light-gray}{2017}

B.A., Psychology, \emph{California State University, Fullerton}
\hfill \textcolor{light-gray}{2015}

\section{PUBLICATIONS}\label{publications}

\textsuperscript{Contribution} \textsuperscript{Notes:}
\textsuperscript{\faLightbulbO} \textsuperscript{=}
\emph{\textsuperscript{Concept/Design}}\textsuperscript{;}
\textsuperscript{\faTable} \textsuperscript{=}
\emph{\textsuperscript{Data}
\textsuperscript{Collection}}\textsuperscript{;}
\textsuperscript{\faBarChart} \textsuperscript{=}
\emph{\textsuperscript{Analysis/Visualization}}\textsuperscript{;}
\textsuperscript{\faPencil} \textsuperscript{=}
\emph{\textsuperscript{Writing}} \newline  \textsuperscript{Paper}
\textsuperscript{Notes:} \textsuperscript{\faRegistered}
\textsuperscript{=} \emph{\textsuperscript{Registered}
\textsuperscript{Report}}\textsuperscript{;}
\textsuperscript{\faCheckCircle} \textsuperscript{=}
\emph{\textsuperscript{Preregistered}}\textsuperscript{;}
\textsuperscript{\faDatabase} \textsuperscript{=}
\emph{\textsuperscript{Open}
\textsuperscript{Dataset}}\textsuperscript{;}
\textsuperscript{\faFileCodeO} \textsuperscript{=}
\emph{\textsuperscript{Open} \textsuperscript{Code}} \newline 
\textsuperscript{Authorship} \textsuperscript{Notes:}
\textsuperscript{\faUnsorted} \textsuperscript{=}
\emph{\textsuperscript{Shared} \textsuperscript{First}
\textsuperscript{Authorship}}

\textcolor{light-gray}{Peer Reviewed Articles}

24.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
Costello, W., Sedlacek, A. G. B., \textbf{Durkee, P. K.}, Crosby, C. L.,
Hahnel-Peeters, R. K., \& Buss, D. M. (in press). Beyond Falsifiability:
Evolutionary Psychology's Many Theoretical Strengths. \emph{American
Psychologist}.

23.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
Costello, W., Sedlacek, A. G. B., \textbf{Durkee, P. K.}, Crosby, C. L.,
Hahnel-Peeters, R. K., \& Buss, D. M. (in press). Evolutionary
psychology hypotheses are testable and falsifiable. \emph{American
Psychologist}.

22.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase \faFileCodeO}} \textbf{Durkee,
P. K.} (2025). Measuring Personality Traits: Simulations Exploring
(Mis)Alignment Between Methods and Measurands. \emph{Journal of Research
in Personality}.

21.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
Alger, I., Gavrilets, S., \textbf{Durkee, P. K.} (2024). Proximate and
Ultimate Drivers of Norms and Norm Change. \emph{Current Opinion in
Psychology}.

20.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faCheckCircle \faDatabase \faFileCodeO}}
Landers, M., Sznycer., D., \textbf{Durkee, P. K.} (2024).
\href{http://www.pdurkee.com/files/pubs/LandersSznycerDurkee2024.pdf}{Are
Self-Conscious Emotions About the Self? Testing Competing Theories of
Shame and Guilt Across Two Disparate Cultures. \emph{Emotion}.}

19.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
\href{https://www.sciencedirect.com/science/article/pii/S1090513824000461?dgcid=author}{\textbf{Durkee,
P. K.}, Lukaszewski, A. L. (2024). Deconstructing ``dominance'' to
refine leadership research. \emph{Evolution and Human Behavior}.}

18.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil\faFileCodeO}}
\href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0303188}{Alberhasky,
M., \textbf{Durkee, P. K.} (2024). Songs Tell a Story: The Arc of
Narrative for Music. \emph{PLoS ONE}.}

17.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
\textbf{Durkee, P. K.} (2023).
\href{http://www.pdurkee.com/files/pubs/Durkee2023_HimbaStatusComment.pdf}{Status
in Himba Pastoralists: Are Causal Claims Warranted? \emph{Evolution and
Human Behavior}.}

16.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} Lukaszewski, A.
W., Patton, J. Q., \textbf{Durkee, P. K.}, Zerbe, J. G., \& Bowser, B.
J. (2023).
\href{http://www.pdurkee.com/files/pubs/PersonalityConambo2023.pdf}{Calibration
and fitness-linked correlates of personality in Conambo, Ecuador.
\emph{Evolution and Human Behavior}.}

15.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faRegistered\faDatabase\faFileCodeO}}
\textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss, D. M. (2023).
\href{https://www.cambridge.org/core/services/aop-cambridge-core/content/view/F16454C7E058347A01F94E64565CBF19/S2513843X23000129a.pdf/status-impact-assessment-is-accuracy-linked-with-status-motivations.pdf}{Status-impact
assessment: Is accuracy linked with status motivations?
\emph{Evolutionary Human Sciences}.}

14.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} Manson, J. H.,
Chua, K. J., Rodriguez, N. N., Barlev, M., \textbf{Durkee, P. K.},
Lukaszewski, A. W. (2023).
\href{http://www.pdurkee.com/files/pubs/Mansonetal_2022.pdf}{Sex
differences in fearful personality traits are mediated by physical
strength. \emph{Social Psychological and Personality Science}.}

13.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} \textbf{Durkee, P.
K.}, Lukaszewski, A. W., von Rueden, C., Gurven, M., Buss, D. M.,
Tucker-Drob, E. M. (2022).
\href{http://www.pdurkee.com/files/pubs/Durkee_etal_2022_PsychScience.pdf}{Niche
diversity predicts personality structure across 115 nations.
\emph{Psychological Science}.}

12.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faRegistered\faDatabase\faFileCodeO}}
Michaelides, M. P., \textbf{Durkee, P. K.} (2021).
\href{http://www.pdurkee.com/files/pubs/Michaelides&Durkee.pdf}{Self-regulation
versus self-discipline in predicting achievement: A replication study
with secondary data. \emph{Frontiers in Education}.}

11.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faRegistered\faDatabase\faFileCodeO}}
\textbf{Durkee, P. K.}, Ayers, J. D. (2021).
\href{http://www.pdurkee.com/files/pubs/Durkee&Ayers2021_fWHR_EHB.pdf}{Is
facial width-to-height ratio reliably associated with social inferences?
\emph{Evolution and Human Behavior}.}

10.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faRegistered\faDatabase\faFileCodeO}}
Crosby, C. L.\textsuperscript{\faUnsorted}, \textbf{Durkee, P.
K.}\textsuperscript{\faUnsorted}, Sedlacek, A. G. B., Buss, D. M.
(2021).
\href{http://www.pdurkee.com/files/pubs/Crosby_et_al-2021-Adaptive_Human_Behavior_and_Physiology.pdf}{Mate
availability and sexual disgust. \emph{Adaptive Human Behavior and
Physiology.}}

9.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} \textbf{Durkee, P.
K.}, Lukaszewski, A. L., Buss, D. M. (2021).
\href{http://www.pdurkee.com/files/pubs/DurkeeReply_2021.pdf}{Reply to
Cheng et al.: Benefit generation dominates cost infliction in explaining
cross-national status allocations. \emph{Proceedings of the National
Academy of Sciences}.}

8.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} \textbf{Durkee, P.
K.},
\href{http://www.pdurkee.com/files/pubs/DurkeeLukaszewskiBuss2020_PsychologicalFoundationsofHumanStatusAllocation.pdf}{Lukaszewski,
A. L., Buss, D. M. (2020). Psychological foundations of human status
allocation. \emph{Proceedings of the National Academy of Sciences}.}

7.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} Lukaszewski, A.
W., Lewis, D. M. G., \textbf{Durkee, P. K.}, Sell, A., Sznycer, D.,
Buss, D. M. (2020).
\href{http://www.pdurkee.com/files/pubs/AnAdaptationistFrameworkPersonality.pdf}{An
adaptationist framework for personality science. \emph{European Journal
of Personality}.}

6.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase\faFileCodeO}} Buss, D.
M.\textsuperscript{\faUnsorted}, \textbf{Durkee, P.
K.}\textsuperscript{\faUnsorted}, Shackelford, T. K., Schmitt, D. P.,
Bowdle, B. F., Brase, G. L., Choe, J. C., Trofimova, I. (2020).
\href{http://www.pdurkee.com/files/pubs/Buss&Durkee_etal_HumanStatusCriteria.pdf}{Human
status criteria: Sex differences and similarities across 14 nations.
\emph{Journal of Personality and Social Psychology}.}

5.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{}} Crosby, C. L., \textbf{Durkee, P. K.},
Meston, C. M., Buss, D. M. (2020).
\href{https://labs.la.utexas.edu/mestonlab/files/2019/12/1-s2.0-S0191886919306543-main.pdf}{Six
dimensions of sexual disgust. \emph{Personality and Individual
Differences}.}

4.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faCheckCircle\faDatabase\faFileCodeO}}
\textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss, D. M. (2019).
\href{http://www.pdurkee.com/files/pubs/DurkeeLukaszewskiBuss_PrideShame_2019.pdf}{Pride
and shame: Key components of a culturally universal status management
system. \emph{Evolution and Human Behavior}.}

3.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faFileCodeO}} \textbf{Durkee, P. K.}
(2019). \href{http://www.pdurkee.com/files/pubs/Durkee_2019.pdf}{Do the
Maasai perceive weak walkers to be stronger and more attractive than
strong walkers? A re-analysis of Fink et al.~(2019). \emph{Biology
Letters}.}

2.\hangindent=0.5in \marginpar{\scriptsize{\faBarChart\faPencil}}
\marginpar{\textsuperscript{}} \textbf{Durkee, P. K.}, Polo, P.,
Munoz-Reyes, J. A., Rodriguez-Ruiz, C., Losada-Perez, M.,
Fernandez-Martinez, A. B., Turiegano, E., Buss, D. M., Pita, M. (2019).
\href{https://journals.sagepub.com/doi/pdf/10.1177/1474704919852918}{Men's
bodily attractiveness: Muscles as fitness indicators. \emph{Evolutionary
Psychology}.}

1.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faTable\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faDatabase}} \textbf{Durkee, P.
K.}\textsuperscript{\faUnsorted}, Goetz, A.
T.\textsuperscript{\faUnsorted}, Lukaszewski, A. W. (2018).
\href{http://www.pdurkee.com/files/pubs/DurkeeGoetzLukaszewski_2018.pdf}{Formidability
assessment mechanisms: Examining their speed and automaticity.
\emph{Evolution and Human Behavior}.}

\textcolor{light-gray}{Edited Volume Contributions}

2.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
\marginpar{\textsuperscript{}} \textbf{Durkee, P. K.} (2024).
\href{https://osf.io/hukwr}{Emotions and Status Hierarchies. In
\emph{The Oxford Handbook of Evolution and the Emotions} (eds.~L.
Al-Shawaf \& T. K. Shackleford). Oxford University Press.}

1.\hangindent=0.5in \marginpar{\scriptsize{\faLightbulbO\faPencil}}
\marginpar{\textsuperscript{}} \textbf{Durkee, P. K.}, Lukaszewski, A.
L. (2023). Pride and the Psychology of Prestige. In \emph{The SAGE
Encyclopedia of Leadership Studies} (eds.~G. R. Goethals, S. T. Allison,
G. J. Sorenson). SAGE Publications.

\textcolor{light-gray}{Preprints and Working Papers}

2.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faFileCodeO}} \textbf{Durkee, P. K.} (2023,
June). \href{http://dx.doi.org/10.2139/ssrn.4482488}{Measuring a
Personality Trait is Harder than I Thought: Simulations Exploring the
Interplay between Measurands, Mechanisms, and Measurement in Personality
Research. \emph{SSRN}.}

1.\hangindent=0.5in
\marginpar{\scriptsize{\faLightbulbO\faBarChart\faPencil}}
\marginpar{\textsuperscript{\faFileCodeO}} \textbf{Durkee, P. K.},
Lukaszewski, A. L., Buss, D. M. (2021, April).
\href{https://psyarxiv.com/4gvt5/}{Status foundations: Further
consideration of the role of `dominance' and the relative importance of
cost infliction and benefit generation. \emph{PsyArXiv}.}

\textcolor{light-gray}{Other Publications}

1. \hangindent=0.5in \textbf{Durkee, P. K.} Instructor's Manual and Test
Bank for \emph{Evolutionary Psychology: The New Science of The Mind}.
Routledge, 2024.

\section{PRESENTATIONS}\label{presentations}

\textsuperscript{\faChevronCircleDown} \textsuperscript{=}
\textsuperscript{Undergraduate} \textsuperscript{Mentee}

\textcolor{light-gray}{Invited Talks}

13. \hangindent=0.5in \textbf{Durkee, P. K.} (March, 2025).
\emph{Differentiating hierarchy navigation emotions}. Talk given at the
Oklahoma Center for Evolutionary Analysis (OCEAN) at OK State.

12. \hangindent=0.5in \textbf{Durkee, P. K.} (February, 2025).
\emph{Linking adaptationist models of emotion to lexical personality
traits}. Talk given at the SPSP Evolutionary Psychology Preconference in
Denver, CO.

11. \hangindent=0.5in \textbf{Durkee, P. K.} (May, 2024). \emph{Linking
adaptationist models of emotion to lexical personality traits}. Talk
given to the Center for Evolutionary Psychology (CEP) at UC Santa
Barbara.

10. \hangindent=0.5in \textbf{Durkee, P. K.} (October, 2023).
\emph{Exploring conceptual overlap between preferences in economics and
personality in pshychology}. Talk given to the CSU Fresno Department of
Economics.

9. \hangindent=0.5in \textbf{Durkee, P. K.} (June, 2023).
\emph{Preferences and Personality}. Talk given to the Institute for
Advanced Study in Toulouse, France.

8. \hangindent=0.5in \textbf{Durkee, P. K.} (March, 2023).
\emph{Improving Personality Measurement}. Talk given to the Center for
the Study of Human Nature, CSU Fullerton.

7. \hangindent=0.5in \textbf{Durkee, P. K.} (September, 2021).
\emph{Cultural Variation in Niche Diversity and Personality Structure}.
Virtual talk given to the Institute for Advanced Study in Toulouse,
France.

6. \hangindent=0.5in \textbf{Durkee, P. K.} (May, 2021). \emph{Adaptive
challenges posed by hierarchies and emotional adaptations}. Virtual talk
given to the Center for the Study of Human Nature, CSU Fullerton.

5. \hangindent=0.5in \textbf{Durkee, P. K.} (October, 2020).
\emph{Differentiating the potential functions of admiration and respect
through task analysis}. Virtual talk given to the Evolutionary
Psychology Lab, CSU Fullerton.

4. \hangindent=0.5in \textbf{Durkee, P. K.} (July, 2020). \emph{Probing
the psychology underpinning human status hierarchies}. Virtual talk
given to the Evolutionary Social Cognition Lab Group, Arizona State
University.

3. \hangindent=0.5in \textbf{Durkee, P. K.} (October, 2019).
\emph{Investigating associations between individual differences in
emotion parameterization and personality}. Talk given to the Cogntiive
Area Meeting, UT Austin.

2. \hangindent=0.5in \textbf{Durkee, P. K.} (May, 2016). \emph{The
ancestral importance of formidability and its lasting impact on modern
social behavior}. Plenary talk given at the 3rd Annual Exploring Darwin
Conference at Palomar College, Palomar, CA.

1. \hangindent=0.5in \textbf{Durkee, P. K.} (April, 2016). \emph{Is
aggression calibrated to self-perceptions of formidability? An empirical
test}. Talk given to the Psi Beta student research club of Mt. San
Antonio Community College, Walnut, CA.

\textcolor{light-gray}{Chaired Symposia}

1. \hangindent=0.5in \textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss,
D. M. (2021, February). \emph{Psychological foundations of status}.
Paper presentation in the symposium, ``Social Status: New Work
Challenging the Status Quo'' (Co-Chair w/ J. Krems), at the Society for
Personality and Social Psychology Virtual Annual Convention.

\textcolor{light-gray}{Podium Presentations}

14. \hangindent=0.5in \textbf{Durkee, P. K.} (2025, February).
\emph{Navigating hierarchies: Cross-national examination of cues
informing status criteria inference}. Podium presentation at the 25th
annual meeting of the Society for Personality and Social Psychology
(SPSP) in Denver, CO.

13. \hangindent=0.5in
\href{https://www.youtube.com/watch?v=CLGuF_fBM0o&list=PL6Fi8qOQlSrj7v5Kj7C_aekqXco9Cnljk&index=9}{\textbf{Durkee,
P. K.} (February, 2024). \emph{Simulations exploring the interplay
between measurands, mechanisms, and measurement in personality
research}. Pre-recorded data blitz presentation for SPSP Personality
Pre-Conference. \faPlay}

12. \hangindent=0.5in \textbf{Durkee, P. K.} (2023, June). \emph{Status
impact assessment: Is accuracy linked with status motives?}. Podium
presentation at the 33rd annual meeting of the Human Behavior and
Evolution Society, Palm Springs. {[}Finalist for Postdoctoral Research
Award{]}

11. \hangindent=0.5in \textbf{Durkee, P. K.} (2021, June). \emph{Niche
Diversity and Personality Structure}. Virtual podium presentation at the
32nd annual meeting of the Human Behavior and Evolution Society,
Virtually Everywhere.

10. \hangindent=0.5in Sell, A., Lukaszewski, A., Chua, K.,
\textbf{Durkee, P. K.}, Sznycer, D. (2021, June). \emph{Cross-cultural
validation of the importance of cues of strength and reproductive value
for male and female bodily attractiveness.} Virtual podium presentation
at the 32nd annual meeting of the Human Behavior and Evolution Society,
Virtually Everywhere.

9. \hangindent=0.5in Chua, K., Rodriguez, N., \textbf{Durkee, P. K.},
Lukaszewski, A., Manson, J. (2021, June). \emph{Sex differences in
fearful personality traits: explained by facultative calibration to
physical strength?} Virtual podium presentation at the 32nd annual
meeting of the Human Behavior and Evolution Society, Virtually
Everywhere.

8. \hangindent=0.5in \textbf{Durkee, P. K.} (2020, July). \emph{Niche
diversity explains differences in personality structure across human
populations.} Virtual podium presentation at the 14th annual California
Workshop on Evolutionary Social Sciences.

7. \hangindent=0.5in \href{https://osf.io/6gp85/}{\textbf{Durkee, P.
K.}, Lukaszewski, A. L., Gurven, M., von Rueden, C., Buss., D. M.,
Tucker-Drob, E. M. (2020, February). \emph{Does niche diversity explain
differences in personality structure across human populations?} Data
blitz at the 18th annual SPSP Evolutionary Psychology Preconference, New
Orleans, LA.\textsuperscript{\faFilePdfO}}

6. \hangindent=0.5in \href{https://osf.io/6enb8/}{\textbf{Durkee, P.
K.}, Buss, D. M. (2019, August). \emph{Fitness interdependence and
emotions of status conferral}. Podium presentation at the 1st annual
Flyover State Scientists Integrating Evolution Conference, Stillwater,
OK.\textsuperscript{\faFilePdfO}}

5. \hangindent=0.5in Crosby, C. L., \textbf{Durkee, P. K.}, Meston, C.
M., Buss, D. M. (2019, August). \emph{Six dimensions of sexual disgust}.
Podium presentation at the 1st annual Flyover State Scientists
Integrating Evolution Conference, Stillwater, OK.

4. \hangindent=0.5in \textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss,
D. M. (2019, June). \emph{Pride and shame: Key components of a
culturally universal status management system}. Podium presentation at
the 31st annual meeting of the Human Behavior and Evolution Society,
Boston, MA.

3. \hangindent=0.5in Lukaszewski, A. W., Lewis, D. M. G.,
\textbf{Durkee, P. K.}, Sell, A., Sznycer, D., Buss, D. M. (2019, May).
\emph{Anger is the mechanistic core of the folk-lexical construct,
``Agreeableness.''} Podium presentation at the the 31st annual meeting
of the Association for Psychological Science, Washington, DC.

2. \hangindent=0.5in \textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss,
D. M. (2018, July). \emph{How humans assess and allocate social status}.
Podium presentation at the 31st annual meeting of the Human Behavior and
Evolution Society, Amsterdam, Netherlands.

1. \hangindent=0.5in \textbf{Durkee, P. K.}, Goetz, A. T., Lukaszewski,
A. L. (2017, June). \emph{Examining the speed and automaticity of
formidability assessment mechanisms}. Podium presentation presented at
the 29th annual meeting of the Human Behavior and Evolution Society,
Boise, Idaho.

\textcolor{light-gray}{Poster Presentations}

33. \hangindent=0.5in Morales\textsuperscript{\faChevronCircleDown}, J.
\textbf{Durkee, P. K.} (2024, April). \emph{Guilt and Personality.}
Poster presented at Western Psychological Association Annual Conference,
San Francisco, CA.

32. \hangindent=0.5in Garcia\textsuperscript{\faChevronCircleDown}, M.,
Gonzalez\textsuperscript{\faChevronCircleDown}, C., \textbf{Durkee, P.
K.} (2024, April). \emph{Pride, Shame, and Personality.} Poster
presented at Western Psychological Association Annual Conference, San
Francisco, CA.

31. \hangindent=0.5in Valadez\textsuperscript{\faChevronCircleDown}, S.,
\textbf{Durkee, P. K.} (2024, April). \emph{Gratitude and Personality.}
Poster presented at Western Psychological Association Annual Conference,
San Francisco, CA.

30. \hangindent=0.5in Ortiz\textsuperscript{\faChevronCircleDown}, S.,
\textbf{Durkee, P. K.} (2024, April). \emph{Anger and Personality.}
Poster presented at Western Psychological Association Annual Conference,
San Francisco, CA.

29. \hangindent=0.5in Ahmed\textsuperscript{\faChevronCircleDown}, H.
\textbf{Durkee, P. K.} (2024, April). \emph{How do dominance and
prestige relate to physical formidability?} Poster presented at Central
California Research Symposium, Fresno, CA.

28. \hangindent=0.5in Morales\textsuperscript{\faChevronCircleDown}, J.
\textbf{Durkee, P. K.} (2024, April). \emph{Guilt and Personality.}
Poster presented at Central California Research Symposium, Fresno, CA.

27. \hangindent=0.5in Gonzalez\textsuperscript{\faChevronCircleDown},
C., Garcia, M., \textbf{Durkee, P. K.} (2024, April). \emph{Pride,
Shame, and Personality.} Poster presented at Central California Research
Symposium, Fresno, CA.

26. \hangindent=0.5in Valadez\textsuperscript{\faChevronCircleDown}, S.,
\textbf{Durkee, P. K.} (2024, April). \emph{Gratitude and Personality.}
Poster presented at Central California Research Symposium, Fresno, CA.

25. \hangindent=0.5in Ortiz\textsuperscript{\faChevronCircleDown}, S.,
\textbf{Durkee, P. K.} (2024, April). \emph{Anger and Personality.}
Poster presented at Central California Research Symposium, Fresno, CA.

24. \hangindent=0.5in \href{https://osf.io/9nk5w/}{\textbf{Durkee, P.
K.} (2024, February). \emph{Links between personality and individual
differences in the functioning of evolved emotion programs.} SPSP
Evolutoinary Psychology Pre-Conference.}

23. \hangindent=0.5in Wilson, A. N., Bechtold, J., \textbf{Durkee, P.
K.} (2023, December). \emph{Program evaluation of a small private
practice providing problem gambling services}. Poster presented at
International Center for Responsible Gaming, Las Vegas, NV.

22. \hangindent=0.5in \textbf{Durkee, P. K.} (2023, May). \emph{How can
we identify the algorithmic form(s) of evolved psychological
mechanisms?} Poster presentation at the 17th annual California Workshop
on Evolutionary Social Sciences.

21. \hangindent=0.5in
\href{http://www.pdurkee.com/files/pubs/geo_psych_poster.pdf}{\textbf{Durkee,
P. K.} (2022, July). \emph{Regional Analysis of Niche Diversity and
Personality Strucutre.} Regional Cultural Differences Conference.}

20. \hangindent=0.5in Landers, M., Sznycer., D., \textbf{Durkee, P. K.}
(2021, June). \emph{Shame and Guilt: Intrapersonal or Interpersonal
Emotions.} Virtual poster presentation at the 32nd annual meeting of the
Human Behavior and Evolution Society, Virtually Everywhere.

19. \hangindent=0.5in Landers, M., Sznycer., D., \textbf{Durkee, P. K.}
(2021, February). \emph{Testing Models of Shame and Guilt}. Poster
presentation at the Society for Personality and Social Psychology
Virtual Annual Convention.

18. \hangindent=0.5in \textbf{Durkee, P. K.} (2021, May).
\emph{Hierarchy Navigation, Emotion Networks, and Fitness
Interdependence.} Virtual poster presentation at the 15th annual
California Workshop on Evolutionary Social Sciences.

17. \hangindent=0.5in Bargotra,
S.\textsuperscript{\faChevronCircleDown}, Diamond
B.\textsuperscript{\faChevronCircleDown}, Duarte H.
L.\textsuperscript{\faChevronCircleDown}, \textbf{Durkee, P. K.},
Lukaszewski, A. L. (2020, July). \emph{Anger closely tracks apparent
undervaluation: Testing the recalibrational theory of anger using an
act-nomination procedure.}
\href{https://baeab2dc-9ca9-4f07-91d9-ca2bf5c551fa.filesusr.com/ugd/e82d4f_4a0dca2931c042a38b24ac60884dd5cd.pdf}{Virtual
poster at the 14th annual California Workshop on Evolutionary Social
Sciences.\textsuperscript{\faFilePdfO}}

16. \hangindent=0.5in Bowen, L.\textsuperscript{\faChevronCircleDown},
\textbf{Durkee, P. K.}, Buss, D. M. (2020, July). \emph{Differential
associations between self-perceived social rank and facets of
machiavellianism.}
\href{https://baeab2dc-9ca9-4f07-91d9-ca2bf5c551fa.filesusr.com/ugd/e82d4f_8e49b4d32561449ca6aa7ac9a82738e9.pdf}{Virtual
poster at the 14th annual California Workshop on Evolutionary Social
Sciences.\textsuperscript{\faFilePdfO}}

15. \hangindent=0.5in Crosby, C. L., \textbf{Durkee, P. K.}, Buss, D.
M., Batres, C., Kitema, H., A., Rezvushkina, T., Seisembekov, T.,
Dontsov, A., Samekin, A., Abdramanova, S., \ldots{} Burtsev, E. (2020,
July). \emph{Sex differences in sexual disgust: A cross-cultural
analysis.}
\href{https://baeab2dc-9ca9-4f07-91d9-ca2bf5c551fa.filesusr.com/ugd/e82d4f_e00c96a9623f40cd95eee2aaad5e59f5.pdf}{Virtual
poster at the 14th annual California Workshop on Evolutionary Social
Sciences.\textsuperscript{\faFilePdfO}}

14. \hangindent=0.5in \href{https://osf.io/uzpj5/}{Yoon,
J.\textsuperscript{\faChevronCircleDown}, \textbf{Durkee, P. K.}, Buss,
D. M. (2019, August). \emph{Relationships between status-seeking and
sociosexuality}. Poster presentation at the 1st annual Flyover State
Scientists Integrating Evolution Conference, Stillwater,
OK.\textsuperscript{\faFilePdfO}}

13. \hangindent=0.5in \href{https://osf.io/6jnz5/}{Mohamed,
M.\textsuperscript{\faChevronCircleDown}, \textbf{Durkee, P. K.}, Buss,
D. M. (2019, August). \emph{Emotions that track others' status gains and
losses}. Poster presentation at the 1st annual Flyover State Scientists
Integrating Evolution Conference, Stillwater,
OK.\textsuperscript{\faFilePdfO}}

12. \hangindent=0.5in \href{https://osf.io/3rv7z/}{Willis,
D.\textsuperscript{\faChevronCircleDown}, \textbf{Durkee, P. K.}, Buss,
D. M. (2019, August). \emph{Individual differences in hierarchy
navigation strategies}. Poster presentation at the 1st annual Flyover
State Scientists Integrating Evolution Conference, Stillwater,
OK.\textsuperscript{\faFilePdfO}}

11. \hangindent=0.5in \textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss,
D. M. (2019, June). \emph{Are pride and shame key components of a
culturally universal status management system?}. Poster presented at the
31st annual meeting of the Association for Psychological Science,
Washington, DC.

10. \hangindent=0.5in \textbf{Durkee, P. K.}, Lukaszewski, A. L., Buss,
D. M. (2019, April). \emph{Pride, Shame, and Personality: An initial
investigation of differential mechanism parameterization as the root of
personality.} Poster presented at the 13th annual California Workshop on
Evolutionary Social Sciences, Fullerton, CA.

9. \hangindent=0.5in Crosby, C. L., \textbf{Durkee, P. K.}, Buss, D. M.
(2019, April). \emph{Mate availability and sexual disgust.} Poster
presented at the 13th annual California Workshop on Evolutionary Social
Sciences, Fullerton, CA.

8. \hangindent=0.5in Acevedo, C.
M.\textsuperscript{\faChevronCircleDown}, \textbf{Durkee, P. K.}, Goetz,
A. T. (2018, May). \emph{The allure of altercations: Fitness-relevant
information captures our attention}. Poster presented at the 12th annual
California Workshop on Evolutionary Social Sciences, Santa Cruz, CA.

7. \hangindent=0.5in \textbf{Durkee, P. K.}, Lukaszewski, A. L. (2017,
May). \emph{Attractiveness assessment across domains}. Poster presented
at the 11th annual California Workshop on Evolutionary and Social
Sciences, San Louis Obispo, CA.

6. \hangindent=0.5in \textbf{Durkee, P. K.}, Goetz, A. T. (2016, July).
\emph{The relationship between formidability and aggression: A
meta-analytic review}. Poster presented at the 28th annual meeting of
the Human Behavior and Evolution Society, Vancouver, Canada. {[}More
studies included and wider scope compared to initial version at APS{]}

5. \hangindent=0.5in \textbf{Durkee, P. K.}, Goetz, A. T. (2016, May).
\emph{Meta-analytic review of the relationship between aggression and
formidability}. Poster presented at the 28th annual Association for
Psychological Science meeting, Chicago, IL.

4. \hangindent=0.5in \textbf{Durkee, P. K.}, Ayers, J., Goetz, A. T.
(2016, May). \emph{Trolley Problems: An important limitation to
consequentialist intuitions triggered by Hamiltonian mechanisms}. Poster
presented at the 10th annual California Workshop on Evolutionary and
Social Sciences, San Louis Obispo, CA.

3. \hangindent=0.5in Ayers, J., \textbf{Durkee, P. K.}, Goetz, A. T.
(2016, May). \emph{Can we be best friends now? Exploring cooperative
aspects of the coordinated condemnation model}. Poster presented at the
10th annual California Workshop on Evolutionary Social Sciences, San
Luis Obispo, CA.

2. \hangindent=0.5in \textbf{Durkee, P. K.}, Romero, G. A., Goetz, A. T.
(2015, May). \emph{Does sickness, injury, or fatigue recalibrate
perceptions of formidability?} Poster presented at the 27th annual Human
Behavior and Evolution Society Conference, Columbia, MO.

1. \hangindent=0.5in \textbf{Durkee, P. K.}, Romero, G. A., Park, J.,
Goetz, A. T. (2015, April). \emph{Spontaneous assessments of
formidability by men}. Poster presented at the 95th annual Western
Psychological Association Conference, Las Vegas, NV.

\section{TEACHING}\label{teaching}

\textcolor{light-gray}{Instructor of Record}

Causal Inference in Psychology (grad seminar)
\hfill \textcolor{light-gray}{Spring 2025}

Undergraduate Honors Seminar
\hfill \textcolor{light-gray}{Fall 2024, Spring 2025}

Personality Psychology
\hfill \textcolor{light-gray}{Fall/Spring 2023, Spring 2024}

Advanced Statistical Methodology in R (online)
\hfill \textcolor{light-gray}{Fall 2021}

\textcolor{light-gray}{Training}

Advancing Inclusive Mentoring (AIM) Program
\hfill \textcolor{light-gray}{Fall 2024} \newline Introduction to
Teaching Online Using QLT \hfill \textcolor{light-gray}{Fall 2023}
\newline Teaching Online @TXST \hfill \textcolor{light-gray}{Fall 2021}
\newline Supervised Teaching in Psychology
\hfill \textcolor{light-gray}{Spring 2020}

\textcolor{light-gray}{Lab Instructor}

Statistics and Research Design
\hfill \textcolor{light-gray}{Fall 2018, 2019}

\textcolor{light-gray}{Teaching Assistant}

Human Sexuality (\textasciitilde500 students per semester, online)
\hfill \textcolor{light-gray}{Spring 2018, 2019, 2020, 2021; Fall 2020}
\newline The Psychology of Language
\hfill \textcolor{light-gray}{Fall 2017} \newline Cognitive Psychology
\hfill \textcolor{light-gray}{Fall/Spring 2015, 2016} \newline Learning
\& Memory \hfill \textcolor{light-gray}{Fall/Spring 2015, 2016} \newline
Research Methods \hfill \textcolor{light-gray}{Fall/Spring 2015, 2016}

\section{GRANTS \& AWARDS}\label{grants-awards}

Besample ``Beyond the West'' Research Grant
\hfill \textcolor{light-gray}{Spring 2023} \newline KindFund Research
Grant \hfill \textcolor{light-gray}{Fall 2021} \newline Graduate School
Continuing Fellowship \hfill \textcolor{light-gray}{Fall 2021} \newline
LBJ CONNECT Fellowship \hfill \textcolor{light-gray}{Spring 2021}
\newline SCORE Secondary Data Replication Analysis Award (x2)
\hfill \textcolor{light-gray}{Fall 2020} \newline Rick and Paula Short
Fellowship \hfill \textcolor{light-gray}{Summer 2020} \newline PSA
Secondary Analysis Challenge Award
\hfill \textcolor{light-gray}{Spring 2020} \newline LBJ CONNECT
Fellowship \hfill \textcolor{light-gray}{Spring 2020} \newline
Psychology Department Travel Award
\hfill \textcolor{light-gray}{Spring 2020} \newline Hixon Graduate
Fellowship in Statistics \hfill \textcolor{light-gray}{Fall 2019}
\newline Rick and Paula Short Summer Research Fellowship
\hfill \textcolor{light-gray}{Summer 2019} \newline Clark Burnham Travel
Grant \hfill \textcolor{light-gray}{Spring 2019} \newline Psychology
Deparmtment Summer Research Award
\hfill \textcolor{light-gray}{Summer 2018} \newline Professional
Development Travel Award \hfill \textcolor{light-gray}{Spring 2018}
\newline Associated Students, Inc.~(ASI) Student Research Grant
\hfill \textcolor{light-gray}{Spring 2016} \newline Human Evolution and
Behavior Society Conference Travel Grant
\hfill \textcolor{light-gray}{Spring 2016} \newline Giles T. Brown
Graduate Student Travel Grant \hfill \textcolor{light-gray}{Spring 2016}
\newline Psychology Department Student Research Travel Award
\hfill \textcolor{light-gray}{Spring 2016}

\section{PROFESSIONAL SERVICE}\label{professional-service}

\textbf{Data Consultant}
\hfill \textcolor{light-gray}{Fall 2023 - Present} \newline Culture of
Schooling Project (PI: Cristine Legare) \newline \emph{Center for
Applied Cognitive Science}, Austin TX

\textbf{Project Analyst}
\hfill \textcolor{light-gray}{Spring 2021}\newline GED program retention
assessment\newline \emph{Goodwill Excel}, Austin TX

\textbf{Data Scientist}
\hfill \textcolor{light-gray}{Spring 2020}\newline Program outcome
evaluation\newline Upper Ninety Positive Youth Development Program,
Austin TX

\textbf{Editorial Assistant}, \emph{Handbook of Human Mating}, Buss, D.
M. (Ed.) \hfill \textcolor{light-gray}{Fall 2019 - Spring 2021}

\textbf{Mentor}, \emph{UTeam}, Mentorship Program for Underrepresented
Students \hfill \textcolor{light-gray}{Fall 2019 - Fall 2020}

\textbf{\emph{Ad hoc}} \textbf{Reviewer:} \newline \emph{Adaptive Human
Behavior and Physiology}; \emph{Aggressive Behavior}; \emph{American
Journal of Human Biology}; \emph{Brain Structure and Function};
\emph{Oxford University Press;} \emph{Evolution and Human Behavior};
\emph{Evolutionary Psychology}; \emph{Evolutionary Psychological
Science}; \emph{Journal of Personality}; \emph{Proceedings of the
National Academy of Science}; \emph{Proceedings of the Royal Academy B};
\emph{PLoS ONE}; \emph{SAGE Open}; \emph{Scandinavian Journal of
Psychology}

\section{TECHNICAL SKILLS}\label{technical-skills}

\textbf{Statistical and Data Management Software:} R, Mplus, LIWC,
Python, JASP, SPSS, EQS, CEFA, Excel, FlexMIRT, MATLAB

\textbf{Stimulus Presentation Software:} formr, PsychoPy, Qualtrics

\section{PROFESSIONAL AFFILIATIONS}\label{professional-affiliations}

Society for Personality and Social Psychology (SPSP) \newline Human
Behavior and Evolution Society (HBES)

\newpage

\section{ACADEMIC REFERENCES}\label{academic-references}

\textbf{David Buss, Ph.D.} \newline Professor of Psychology \newline The
University of Texas at Austin \newline Email:
\href{mailto:dbuss@austin.utexas.edu}{\nolinkurl{dbuss@austin.utexas.edu}}

\textbf{Cristine Legare, Ph.D.} \newline Professor of Psychology
\newline The University of Texas at Austin \newline Email:
\href{mailto:legare@austin.utexas.edu}{\nolinkurl{legare@austin.utexas.edu}}

\textbf{Aaron Lukaszewski, Ph.D.} \newline Associate Professor of
Psychology \newline California State University, Fullerton \newline
Email:
\href{mailto:alukaszewski@fullerton.edu}{\nolinkurl{alukaszewski@fullerton.edu}}

\textbf{Elizabeth Pillsworth, Ph.D.} \newline Professor of Anthropology
\newline California State University, Fullerton \newline Email:
\href{mailto:epillsworth@fullerton.edu}{\nolinkurl{epillsworth@fullerton.edu}}

\textbf{Elliot Tucker-Drob, Ph.D.} \newline Professor of Psychology
\newline The University of Texas at Austin \newline Email:
\href{mailto:tuckerdrob@utexas.edu}{\nolinkurl{tuckerdrob@utexas.edu}}

\end{document}